Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-11-09 doc/paper.tex
fix it for bixit

Another potential improvement, perhaps the most obvious one, is to utilize a better LLM for generating responses, both for reward shaping and policy influencing. The one we used, the 7B model of Llama 2, varies greatly in the quality of responses it produces, as demonstrated in \ref{llmresponse}. While is cost-effective both financially and in terms of computational resources, we expect that better results can be achieved with higher-performance models. This is especially true for policy influencing, where performance depends heavily on the LLM understanding the environment in detail.

>>>>

Another potential improvement, perhaps the most obvious one, is to utilize a better LLM for generating responses, both for reward shaping and policy influencing. The one we used, the 7B model of Llama 2, varies greatly in the quality of responses it produces, as demonstrated in \ref{llmresponse}. While it is cost-effective both financially and in terms of computational resources, we expect that better results can be achieved with higher-performance models. This is especially true for policy influencing, where performance depends heavily on the LLM understanding the environment in detail.
